---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HarmoToolkitNEAR

<!-- badges: start -->
<!-- badges: end -->

The goal of `HarmoToolkitNEAR` is to reduce the repetitive work during harmonization, especially for data cleaning and inspecting.

## Installation

You can install the development version of HarmoToolkitNEAR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Bolin-Wu/HarmoToolkitNEAR")
```

## Example

This is a basic example which shows you how to solve a common problem of transforming sav files to csv files:

```{r example, eval=FALSE}
library(HarmoToolkitNEAR)
## basic example code
sav_to_csv("original_data", "SNAC-K")
```

After running this, there should be a new folder "csv_format" storing the transformed SNAC-K csv files in your current working directory, "original_data/SNAC-K".


